%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{lmodern}
\usepackage{microtype}
\usepackage{fontawesome5}

% Customize icon link
% usage: \iconlink[<icon:fontawesome>][<text>]{<url>}
\NewDocumentCommand{\iconlink}{ o o m }{
  \IfNoValueTF{#1}{
    \let\icon\faLink
  }{
    \let\icon#1
  }
  \IfNoValueTF{#2}{
    \hspace{-12pt}\underline{\href{#3}{\icon}}
  }{
    \hspace{-12pt}\underline{\href{#3}{\icon\ #2}}
  }
  \hspace{-8pt}
}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\firstname{Zhuohua} % Your first name
\familyname{Li} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
%\title{Resume}
\address{The Chinese University of Hong Kong, Shatin, N.T., Hong Kong SAR}{}
\phone[mobile]{(+852)~6587~3796}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{zhli@cse.cuhk.edu.hk}
\homepage{zhuohua.me}
\social[github]{lizhuohua}
\social[linkedin]{lizhuohua}
\social[googlescholar]{lizhuohua}
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------
\vspace*{-5mm}
\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace*{-10mm}
\section{EDUCATION}
\cventry{Aug.2017--Aug.2022}{Ph.D. in Computer Science and Engineering}{The Chinese University of Hong Kong}{Hong Kong}{}{Advanced Networking and System Research Laboratory (ANSRLab)\\ Supervised by Prof. John C.S. Lui}

\cventry{Aug.2013--Jun.2017}{B.E. in Computer Science and Technology}{University of Science and Technology of China}{Hefei}{}{Hua Xia Talent Program in Computer Science and Technology}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{EXPERIENCE}
\cventry{Aug.2023--Present}{Supervisor: Prof. John C.S. Lui}{Postdoctoral Fellow at The Chinese University of Hong Kong}{Hong Kong}{}
{
  \cvlistitem{Working on online learning and multi-armed bandits algorithms and their applications}
}
\cventry{Oct.2022--Aug.2023}{Supervisor: Prof. John C.S. Lui}{Junior Research Assistant at The Chinese University of Hong Kong}{Hong Kong}{}
{
  \cvlistitem{Designing Border Gateway Protocols (BGP) for quantum networks}
  \cvlistitem{Leveraging online learning algorithms to select high-fidelity paths while minimizing the testing cost}
}
\cventry{Jul.2018--Oct.2018}{Supervisor: Dr. Tao  (Lenx) Wei}{Secure Linux Kernel Module Development in Rust}{Baidu X-Lab, USA}{}
{
  \cvlistitem{Developed a framework for writing Linux kernel modules in the Rust programming language}
  \cvlistitem{Provided infrastructures for safe kernel memory allocation and concurrency management}
}

\cventry{Jul.2016--Sep.2016}{Social Computing Group}{Sentiment Analysis of Microsoft's Chatbot XiaoIce}{Microsoft Research Asia, Beijing}{Mentor: Dr. Xing Xie}
{
 	\cvlistitem{Participated in improving the sentiment recognition of XiaoIce, Microsoft's AI chatbot}
  \cvlistitem{Optimized the emotion recognition according to the context of XiaoIce's dialogues}
}

\cventry{Jun.2016}{Advisor: Prof. Hong An}{2016 ISC-HPCAC Student Cluster Competition}{Frankfurt, Germany}{}{
  \cvlistitem{Built an HPC cluster with our team based on \emph{Huawei FusionServer X6800}}
  \cvlistitem{Optimized the performance of several benchmarks and applications within 3kW power-dissipation}
  \cvlistitem{Ranked 4\textsuperscript{th} in overall score and 1\textsuperscript{st} in \emph{WRF (Weather Research and Forecasting Model)}}
}

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
% ----------------------------------------------------------------------------------------
\section{PUBLICATIONS \textnormal{\normalsize (* means equal contribution, \# means corresponding author)}}

\cvlistitem{Maoli Liu, \textbf{Zhuohua Li}\textsuperscript{\#}, Xuchuang Wang, and John C.S. Lui. \textsc{LinkSelFiE}: Link Selection and Fidelity Estimation in Quantum Networks. In \textit{Proceedings of the IEEE Conference on Computer Communications 2024}. INFOCOM '24.}

\cvlistitem{Maoli Liu\textsuperscript{*}, \textbf{Zhuohua Li}\textsuperscript{*\#}, Kechao Cai, Jonathan Allcock, Shengyu Zhang, and John C.S. Lui. Quantum BGP with Online Path Selection via Network Benchmarking. In \textit{Proceedings of the IEEE Conference on Computer Communications 2024}. INFOCOM '24.}

\cvlistitem{Jincheng Wang, \textbf{Zhuohua Li}, Mingshen Sun, Bin Yuan\textsuperscript{\#}, and John C.S. Lui. \href{https://doi.org/10.1109/DSN58367.2023.00053}{IoT Anomaly Detection Via Device Interaction Graph}. In \textit{Proceedings of the 53rd Annual IEEE/IFIP International Conference on Dependable Systems and Network}. DSN '23.}

\cvlistitem{\textbf{Zhuohua Li}, Jincheng Wang, Mingshen Sun, and John C.S. Lui. \href{https://doi.org/10.1007/978-3-031-17143-7_33}{Detecting Cross-Language Memory Management Issues in Rust}. In \textit{Proceedings of the 27th European Symposium on Research in Computer Security}. ESORICS '22.}

\cvlistitem{Jincheng Wang, \textbf{Zhuohua Li}, John C.S. Lui, and Mingshen Sun. \href{https://doi.org/10.1145/3545948.3545953}{Zigbee's Network Rejoin Procedure for IoT Systems: Vulnerabilities and Implications}. In \textit{Proceedings of the 25th International Symposium on Research in Attacks, Intrusions and Defenses}. RAID '22.}

\cvlistitem{Jincheng Wang, \textbf{Zhuohua Li}, John C.S. Lui, and Mingshen Sun. \href{https://doi.org/10.1016/j.cose.2021.102552}{Topology-Theoretic Approach To Address Attribute Linkage Attacks In Differential Privacy}. \textit{Computers \& Security}, Volume 113, February 2022.}

\cvlistitem{\textbf{Zhuohua Li}, Jincheng Wang, Mingshen Sun, and John C.S. Lui. \href{https://doi.org/10.1145/3460120.3484541}{\textsc{MirChecker}: Detecting Bugs in Rust Programs via Static Analysis}. In \textit{Proceedings of the 28th ACM Conference on Computer and Communications Security}. CCS '21.}

\cvlistitem{Jincheng Wang, \textbf{Zhuohua Li}, John C.S. Lui, and Mingshen Sun. \href{https://doi.org/10.1109/INFOCOMWKSHPS51825.2021.9484499}{Topology-Theoretic Approach To Address Attribute Linkage Attacks In Differential Privacy}. In \textit{Proceedings of IEEE INFOCOM WKSHPS: BigSecurity 2021: International Workshop on Security and Privacy in Big Data}. BigSecurity '21.}

\cvlistitem{\textbf{Zhuohua Li}, Jincheng Wang, Mingshen Sun, and John C.S. Lui. \href{https://doi.org/10.1145/3339252.3340506}{Securing the Device Drivers of Your Embedded Systems: Framework and Prototype}. In \textit{Proceedings of the 3rd International Workshop on Security and Forensics of IoT (in conjunction with ARES 2019)}. IoT-SECFOR '19.}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------
\section{SELECTED PROJECTS}
\cvitemwithcomment{\textsc{FFIChecker} (\faIcon[regular]{star}34)}{A Tool for Detecting Cross-Language Memory Management Issues in Rust}{\iconlink[\faGithub]{https://github.com/lizhuohua/rust-ffi-checker}}
  \cvlistitem{Detected memory management issues across Rust's \textit{Foreign Function Interface (FFI)}}
  \cvlistitem{Detected 34 real-world bugs}

\cvitemwithcomment{\textsc{MirChecker} (\faIcon[regular]{star}109)}{A Static Analysis and Bug Detection Tool for Rust programs}{\iconlink[\faGithub]{https://github.com/lizhuohua/rust-mir-checker}}
  \cvlistitem{Performed static analysis on the Rust's \textit{Mid-level Intermediate Representation (MIR)} based on the theory of \textit{Abstract Interpretation}}
  \cvlistitem{Detected 33 real-world runtime panics and memory safety bugs}

\cvitemwithcomment{linux-kernel-module-rust (\faIcon[regular]{star}630)}{A Framework for Secure Kernel Module Development in Rust}{\iconlink[\faGithub]{https://github.com/lizhuohua/linux-kernel-module-rust}}
  \cvlistitem{A framework for writing Linux kernel modules in the Rust programming language}
  \cvlistitem{Provided infrastructures for safe kernel memory allocation and concurrency management}

% \cventry{Sep.2015--Feb.2016}{Advisor: Assoc. Prof. Yu Zhang}{A Simple C Language Compiler based on LLVM}{USTC}{}
% {
% 	\begin{itemize}
% 		\item A mini C compiler implemented using \emph{Flex}+\emph{Bison}+\emph{LLVM}
% 		\item Supports Clang-style informative error messages
% 		\item Supports compiling multiprocess programs using  \textit{Message Passing Interface (MPI)}
% 	\end{itemize}
% }

% \cventry{Mar.2015--Jul.2015}{Advisor: Assoc. Prof. Xi Li}{FPGA Implementation of a MIPS16e Processor}{USTC}{}
% {
% 	\begin{itemize}
% 		\item A processor which supports all \emph{MIPS16e} instructions implemented on \emph{Xilinx FPGA} with \emph{Verilog HDL}
% 		\item Provides a debug module through \emph{RS-232} which can print debug information on a screen
% 	\end{itemize}
% }

% \cventry{Mar.2015--Jun.2015}{Advisor: Assoc. Prof. Kai Xing}{Porting Inferno Operating System to Samsung S3C6410}{USTC}{}
% {
% 	\begin{itemize}
% 		\item Implemented the bootloader, serial port driver and LCD driver  in both \emph{Plan 9} assembly language and C
% 		%	\item Compiled the OS kernel using the ARM cross compiler and loaded it into the memory according to the memory model of S3C6410
% 		%	\item Debugged the code and finished the porting program successfully
% 	\end{itemize}
% }

%----------------------------------------------------------------------------------------
% TEACHING SECTION
%----------------------------------------------------------------------------------------
\section{TEACHING ASSISTANT}
\cvitem{}{CMSC5735: Advanced Topics in Cloud Computing \hfill Spring 2018, \textbf{CUHK}}
\cvitem{}{CSCI3320: Fundamentals of Machine Learning \hfill Spring 2018, \textbf{CUHK}}
\cvitem{}{CSCI2040: Introduction to Python \hfill Fall 2017, \textbf{CUHK}}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------

%\section{EXTRACURRICULAR ACTIVITIES}
%
%\cvitem{Sep.2013--Jun.2015}{Minister, Department of Sports, Student Union}
%\cvitem{Sep.2013--Jun.2017}{Member of Linux User Group, USTC}
%\cvitem{Oct.2013}{Volunteer of Special Education Center in Hefei}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{HONORS \& AWARDS}
\cvitem{}{Second-class Scholarship for Outstanding Student (10\%) for two times \hfill Sep.2015--Sep.2016, \textbf{USTC}}
\cvitem{}{A-Sponsorship of Talent Class Plan (10\%) for three times \hfill Sep.2014--Sep.2016, \textbf{USTC}}
\cvitem{}{Excellent Student Cadre (3\%) \hfill Sep.2015, \textbf{USTC}}
\cvitem{}{Third-class Scholarship for Outstanding Student (15\%) \hfill Sep.2014, \textbf{USTC}}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{COMPUTER SKILLS}
\cvitemwithcomment{Operating Systems}{Gentoo Linux, macOS}{}
\cvitemwithcomment{Programming Languages}{Experienced in C/C++, Rust, Python}{}
\cvitemwithcomment{Editors}{Emacs, Vim}{}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

%\section{Languages}

%\cvitemwithcomment{English}{Mothertongue}{}
%\cvitemwithcomment{Spanish}{Intermediate}{Conversationally fluent}
%\cvitemwithcomment{Dutch}{Basic}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Piano}{Chess}
%\cvlistdoubleitem{Cooking}{Dancing}
%\cvlistitem{Running}

%----------------------------------------------------------------------------------------

\end{document}

%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-master: t
%%% TeX-engine: default
%%% End:
